Community-Conditioned Language Models

### 2020-11-23 paper/paper.tex
formula for ppl

We measure the perplexity of each example\jp{message? community?} in the test set. 
For this, we use the negative exponential of the mean cross-entropy loss 
of the language model for a given message and average over a set of messages, $M$.
\[\Ppl_M = \avg_{m\in M}(-e^{H(m)})\]
\bn{Following the logic from IG, should we change Ppl to the exponential of the average cross entropy, rather than using the average of the message-level perplexity?}
\jp{Yes}
As one would expect, 
the conditioned models have lower perplexity
than their respective unconditioned baseline models (\cref{tab:model-results}),
but this effect is different in magnitude
for models with different community embedding depths.
For the LSTM encoder, 
the best model ($l_c=1$) concatenates the community embedding after the first encoder layer,
with two subsequent LSTM layers. 
The best transformer model ($l_c=3$), on the other hand,
incorporates the community information last,
after all the sequence encoder layers.

>>>>

We measure the perplexity of each example\jp{message? community?} in the test set. 
For this, we use the negative exponential of the mean cross-entropy loss 
of the language model for a given message and average over a set of messages, $M$.
\[\Ppl_M = \avg_{m\in M}(e^{-H(m)})\]
\bn{Following the logic from IG, should we change Ppl to the exponential of the average cross entropy, rather than using the average of the message-level perplexity?}
\jp{Yes}
\[\Ppl_M = e^{\avg_{m\in M} H(m)}\]
As one would expect, 
the conditioned models have lower perplexity
than their respective unconditioned baseline models (\cref{tab:model-results}),
but this effect is different in magnitude
for models with different community embedding depths.
For the LSTM encoder, 
the best model ($l_c=1$) concatenates the community embedding after the first encoder layer,
with two subsequent LSTM layers. 
The best transformer model ($l_c=3$), on the other hand,
incorporates the community information last,
after all the sequence encoder layers.
